A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-03-23 faculty.tex
Updates from Overleaf

\section{The 5 jobs of an assistant professor}
An tenure-track professor in CS (and likely in other fields) at an R1 university typically has \emph{five} jobs:

>>>>

\section{The 5 jobs of an assistant professor}
An tenure-track professor in CS (and likely in other STEM fields) at an R1 university typically has \emph{five} jobs:
